Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-16 manuscript.Rmd
Updating small multiples.

# sm.scopus.merged.table <- group_by(sm.scopus.merged, Journal) %>%
#     summarize(DataBase.N = sum(N, na.rm=TRUE), Scopus.N = sum(Documents, na.rm=TRUE)) %>%
#     arrange(desc(DatabBase.N))
# 
# data.frame(sm.scopus.merged.table)

# abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
# abb$ID <- 1:nrow(abb)
# sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
#     select(-X) %>%
#     mutate(Documents = ifelse(Documents == 0, NA, Documents))
# 
# # Re-order the factor by Overall.N
# title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
#     distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()
# 
# title.order = title$Abbrev
# 
# sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
# 
# # Create labels for the facets
# Overall.N <- distinct(sm.scopus.merged, Abbrev) 
# lab <- paste("N=", Overall.N$Overall.N, sep="")
# #xpos = rep(2002, 79)
# #ypos = rep(215, 79)
# xpos = rep(2025, 79)
# ypos = rep(25, 79)
# ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
#     rename(Abbrev = Overall.N.Abbrev) 
#

# Plotting function    
# plotSmallMultiples <-  ggplot(sm.scopus.merged,  aes(Year, N)) + geom_line(colour="#e66101") +
#     facet_wrap(~ Abbrev) + 
#     geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99", alpha=.60) + 
#     theme_bw() +
#     theme(legend.position = "bottom", 
#     panel.grid.minor = element_blank(), 
#     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
#     geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3) + 
#     ylim(c(0,225)) +
#     scale_x_continuous(breaks=seq(1989, 2015, 8)) + 
#     expand_limits(x = 2050))

@@

@@

>>>>

 sm.scopus.merged.table <- group_by(sm.scopus.merged, Journal) %>%
     summarize(DataBase.N = sum(N, na.rm=TRUE), Scopus.N = sum(Documents, na.rm=TRUE)) %>%
     arrange(desc(DataBase.N))

 abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
 abb$ID <- 1:nrow(abb)
 sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
     select(-X) %>%
     mutate(Documents = ifelse(Documents == 0, NA, Documents))

 # Re-order the factor by Overall.N
 title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
     distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()

 title.order = title$Abbrev

 sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
# 
 # Create labels for the facets
 Overall.N <- distinct(sm.scopus.merged, Abbrev) 
 lab <- paste("N=", Overall.N$Overall.N, sep="")
 xpos = rep(2002, 79)
 ypos = rep(215, 79)
 ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
     rename(Abbrev = Overall.N.Abbrev)

 titles.reduced <- unique(sm.scopus.merged$Journal)
 titles.reduced.1 <- titles.reduced[1:40]
 titles.reduced.2 <- titles.reduced[41:length(titles.reduced)]

# Plotting function    
 plotSmallMultiples.1 <-  ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ],  aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ], aes(Year, Documents)) + 
     facet_wrap(~ Abbrev) + 
     theme_bw() +
     theme(strip.text.x = element_text(size = 8)) + 
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
     geom_text(data = ldata[1:40, ], aes(x =xpos, y = ypos, label = lab), size =3) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8))

plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], aes(Year, Documents)) + 
     facet_wrap(~ Abbrev) + 
     theme_bw() +
     theme(strip.text.x = element_text(size = 8)) +  
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =3) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8))

@@

A total of XX article records from XX unique journal titles met the inclusionary
criteria and were included in the historical database.

Figure 1 uses a
small multiples plot to summarize the number of article records for each year
throughout the study period.  Small multiples, also referred to as trellis
and lattice charts, are the best design solution for visually enforcing comparisons of
change (Tufte, XXXX).  In this context, we use two different data sources to show differences in publishing across the journals -- the orange line represents data from the SWHD, and the purple line represents data from Scopus.

the small multiples to show differences in publishing across the journals,

show differences in publication history for each journal.

The number of article records for each year (by journal) is denoted by an orange line, along with the overall number of article records.  For further contextual information, the number of article records available from Scopus is presented with a purple line.   
This plot reveals variability in publishing over time and across journals.  The for each journal and across journals.  
First, the historical database indexed XX journals, whereas Scopus indexed only XX.  For the number of journals indexed by Scopus, the number of article records tend to be higher than the number of records available in the historical database.  The primary reason for this difference is that Scopus included editorials and book reviews in their summary data, whereas these were excluded from the SWHD.  Other difference can be attributed to errors and gaps in indexing across both databases.  As we relied upon aggregate data from Scopus, we were unable to quantify these differences.

should be noted that the number of article records available from Scopus tends to be greater than the historical database because Scopus included editorials (AND REVIEWS), whereas these were excluded from the historical database.

According to Tufte (Evisioning information), small multiples are the best design s

@@

\newpage
```{r fig.height=10, fig.width=7.5}
plotSmallMultiples.1

\newpage
```{r fig.height=10, fig.width=7.5}
plotSmallMultiples.2

```
\newpage
